Models

### 2023-01-17 analysis/05_model_metrics.Rmd
fix copy paste issues in outlier section

# get info for how original models were fit
outlier_mods <- trans_model_df %>% 
  select(start_mod = model, metric_name = metric, lmer_formula = formula, REML, bobyqa) %>%
  right_join(criterion) %>%
  select(start_mod, metric_name, outlier_criterion, lmer_formula, REML, bobyqa)

@@

Fit models for studies with only one time series
```{r}

#get dataframe of glm's to fit
glm_indv_model_df <- single_ts %>% 
  mutate(model_id = "base",
         formula = case_when(
           metric_name %in% raw_metrics ~ "value ~ year_scaled",
           metric_name %in% log_metrics ~ "log(value) ~ year_scaled",
           TRUE ~ "logvalue ~ year_scaled"
           )
         )

>>>>

unique_mod_df <- model_table %>%
  filter(model_id == "base") %>%
  select(metric, model, model_id, formula, REML, bobyqa) %>%
  group_by(metric) %>% 
  slice_head() %>%
  ungroup()

# get info for how original models were fit
outlier_mods <- unique_mod_df %>% 
  select(start_mod = model, metric_name = metric, lmer_formula = formula, REML, bobyqa) %>%
  right_join(criterion) %>%
  select(start_mod, metric_name, outlier_criterion, lmer_formula, REML, bobyqa)

@@

Fit models for studies with only one time series
```{r}
#get dataframe of glm's to fit
glm_indv_model_df <- single_ts %>% 
  mutate(model_id = "base",
         formula = case_when(
           metric_name %in% raw_metrics ~ "value ~ year_scaled",
           metric_name %in% log_metrics ~ "log(value) ~ year_scaled",
           TRUE ~ "logvalue ~ year_scaled"
           )
         )
